---
title: "Q10_redo"
author: "Todd Garner"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Last Question - *Use the EducationIncome.csv dataset to visually test the claim that the distribution of incomes increase (mean or median) as the education level rises.*

First, I'll load in the dataset and take a look at what we've got.  


```{r}
Ed <- read.csv("/Users/tgarn/OneDrive/Desktop/SMU - MS Data Science/Courses/GitHub/DS_6306_weekly_assignments/Week_2/DS6306_week2/Education_Income.csv", header = TRUE)
head(Ed)

#Let's explore how many unique values we have in the Educ column

unique(Ed$Educ, incomparables = FALSE)
```
Seeing that there are 5 unique timesframes in years, I believe that the most straightforward method, given the remaining time, would be to use these characters to select the values for rising years in education and compare it against Income.  I think we can discard the values "<12" and just go with "12" and compare that to "13-15", "16" and ">16". 

```{r}
Ed <- read.csv("/Users/tgarn/OneDrive/Desktop/SMU - MS Data Science/Courses/GitHub/DS_6306_weekly_assignments/Week_2/DS6306_week2/Education_Income.csv", header = TRUE)
head(Ed)

data_less_12 <- Ed[Ed$Educ == "<12",]
#head(data_lew_12)
#summary(data_less_12)
E_less_12 <- data.frame(data_less_12$Income2005)

#mean(data_less_12$Income2005)
#summary(E_less_12)
data_12 <- Ed[Ed$Educ == "12",]
#head(data_12)
#summary(data_12)
E12 <- data.frame(data_12$Income2005)
#mean(data_12$Income2005)
#summary(E12)
data_13_15 <- Ed[Ed$Educ == "13-15",]
#head(data_13_15)
E_13_15 <- data.frame(data_13_15$Income2005)
#head(E_13_15)
#summary(E_13_15)
data_16 <- Ed[Ed$Educ == "16",]
#head(data_16)
E_16 <- data.frame(data_16$Income2005)
#head(E_16)
#summary(E_16)
data_over_16 <- Ed[Ed$Educ == ">16",]
#head(data_over_16)
E_over_16 <- data.frame(data_over_16$Income2005)
#head(E_over_16)
#summary(E_over_16)

ZA <- mean(data_less_12$Income2005)
A <- mean(data_12$Income2005)
B <- mean(E_13_15$Income2005)
C <- mean(data_16$Income2005)
D <- mean(data_over_16$Income2005)

mean_vec <- c("ZA", "A", "B", "C", "D")
mean_vec_df = data.frame(mean_vec)
head(mean_vec_df)
data_vec <- c("E_less_12", "E12", "E_13_15", "E_16", "E_over_16")
data_vec_df <- data.frame(data_vec)
head(data_vec_df)
label_vec <- c("<12", "12", "13-15", "16", ">16")
label_vec_df <- data.frame(label_vec)
head(label_vec_df)

boxplot(,  ~ mean_vec, data = Ed, notch = TRUE, add = TRUE, col = "blue", log = "y")

plot(label_vec, mean_vec, type = "p") #View(mean_vec)

paste(D)
#mean_vec %>%
#  ggplot(aes(

#geom_hline()
```
The medians show that with rising education there is a strong suggestion that incomes also rise.  


*I'm not happy with my work on this Live Set 2 at all.  It's beneath my quality standards.  I spent countless hours spinning my wheels.  I've got to do better in finding solutions.  I took shortcuts with the modifying the dataset early on and didn't have time to come back and change it, even though I figured out how to do so.  I'm embarrassed to turn this in.  I clearly have a lot of work to do in order to be more efficient with my time.  My apologize to the professor for this subpar work.  








